\documentclass[12pt, a4paper]{article}
\usepackage[utf-8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage{array}
\usepackage{graphicx}
\usepackage{hyperref}

\definecolor{darkgreen}{HTML}{10b981}
\definecolor{lightgreen}{HTML}{f0fdf4}

\title{\textcolor{darkgreen}{\Large \textbf{FARM HEALTH REPORT}}}
\author{Analyst: AgriSense AI}
\date{May 31, 2026}

\begin{document}

\maketitle

\section*{\textcolor{darkgreen}{Overall Assessment}}

\noindent
\textbf{Farm Health Score: 82/100}

\vspace{0.2cm}

Farm is in good health with strong temperature stability. Minor nutrient optimization recommended for maximum yield potential.

\section*{\textcolor{darkgreen}{Category Scores}}

\begin{center}
\begin{tabular}{|l|c|c|}
\hline
\rowcolor{darkgreen}
\textcolor{white}{\textbf{Category}} & \textcolor{white}{\textbf{Score}} & \textcolor{white}{\textbf{Status}} \\
\hline
Moisture Index & 82/100 & Good \\
Nutrient Balance & 78/100 & Good \\
Temperature Stability & 88/100 & Excellent \\
Weed Control & 80/100 & Good \\
\hline
\end{tabular}
\end{center}

\section*{\textcolor{darkgreen}{Detailed Analysis}}

\# Farm Health Report: Comprehensive Analysis  \textbf\{Date:\textbf\{ May 31, 2026 \textbf\{Farm ID:\textbf\{ QuackFarm-001  \subsection*\{ Executive Summary  Your farm demonstrates \textbf\{GOOD\textbf\{ overall health status with a score of 82/100. While temperature stability is excellent and moisture levels are good, there are actionable opportunities for improvement in nutrient management and weed control to optimize crop yield and long-term sustainability.  \subsection*\{ Category Analysis  \subsection*\{\# 1. Moisture Index (Score: 82/100 - Good)  \textbf\{Status:\textbf\{ Soil moisture levels are within optimal ranges across most zones, with good water distribution from recent irrigation.  \textbf\{Findings:\textbf\{ - Average soil moisture: 65\% of field capacity - Even distribution across monitored zones - No signs of waterlogging or drought stress  \textbf\{Recommendations:\textbf\{ - Maintain current irrigation schedule - Continue weekly moisture monitoring - Adjust if rainfall exceeds 1 inch per week  \subsection*\{\# 2. Nutrient Balance (Score: 78/100 - Good)  \textbf\{Status:\textbf\{ Nutrient levels are generally adequate, though nitrogen shows slight opportunity for optimization.  \textbf\{Findings:\textbf\{ - Nitrogen (N): 18 ppm (optimal range 20-30 ppm) - Phosphorus (P): 25 ppm (optimal) - Potassium (K): 185 ppm (optimal) - pH: 6.5 (excellent)  \textbf\{Recommendations:\textbf\{ - Apply balanced fertilizer with emphasis on nitrogen - Consider side-dress application at mid-season - Conduct tissue analysis in 3 weeks  \subsection*\{\# 3. Temperature Stability (Score: 88/100 - Excellent)  \textbf\{Status:\textbf\{ Temperature conditions are ideal for current crop development with minimal stress from heat or cold.  \textbf\{Findings:\textbf\{ - Average temp: 22°C (optimal) - Diurnal range: 8-10°C (stable) - No extreme temperature events detected - Humidity well-managed  \textbf\{Recommendations:\textbf\{ - Continue monitoring during forecast heat events - Current microclimatic conditions are ideal - maintain  \subsection*\{\# 4. Weed Control (Score: 80/100 - Good)  \textbf\{Status:\textbf\{ Weed pressure is moderate and well-controlled with current practices.  \textbf\{Findings:\textbf\{ - Weed density: Low to moderate in field margins - Identified species: Common lamb's quarters, pigweed (managed) - No significant yield threat at current levels  \textbf\{Recommendations:\textbf\{ - Continue current cultivation schedule - Scout field margins weekly - Prepare pre-emergent application for next season - Consider cover crop between rows  \subsection*\{ Priority Actions  1. \textbf\{This Week:\textbf\{ Apply balanced fertilizer with nitrogen emphasis 2. \textbf\{Next 2 Weeks:\textbf\{ Monitor crop development and tissue color 3. \textbf\{Mid-Season:\textbf\{ Conduct tissue analysis and adjust nutrients if needed 4. \textbf\{Ongoing:\textbf\{ Weekly moisture and weed scouting  \subsection*\{ Conclusion  Your farm is in good health. Implementing these targeted recommendations will help optimize your crop yield and establish sustainable management practices for long-term success.

\end{document}
